\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs} % To thicken table lines
\usepackage{comment}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Replication: Discovering Value from Community Activity on Focused Question Answering Sites: A Case Study of Stack Overflow\\
%\thanks{Final project report for CISC 880.}
\thanks{Group assignment for CISC 880.}
}

\author{\IEEEauthorblockN{Aaditya Bhatia, Abdullah Ahmad Zarir, Daniel Lee, Kundi Yao, Md Hasan Ibrahim}
\IEEEauthorblockA{\textit{Software Analysis and Intelligence Lab (SAIL)} \\
\textit{Queen's University}\\
Kingston, Canada \\
\{aaditya.bhatia, a.zarir, 18dil, 18ky10, ibrahim.mdhasan\}@queensu.ca}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
}

\maketitle

\begin{abstract}

Question-answering (Q\&A) websites offer a plethora of meaningful knowledge that remains untapped. Prior studies mainly focused on providing the best answer to the questioner. However, there is a shift towards extrapolating value for a broader audience by analyzing community dynamics. The voting and reputation feature of Q\&A sites ensure the accuracy and quality of the content.


In our paper, we focused on questions with their corresponding set of answer, rather than individual question-answer pairs. In addition, we used reputation to find information about levels of community involvement and incentives for successful contributions and positive behavior. We considered the dynamics of the community activity from a question and full site level that shaped the set of answers, how answers and votes arrive over time and how the dynamics influence the outcome. We formulated two prediction tasks to help us predict the long-lasting value of a question and predict whether a question has been sufficiently answered. Based on the high performance of our prediction tasks, we concluded that there are certain features in community dynamics on Stack Overflow that can provide valuable information.

\input{tex/abstract}
\end{abstract}


\hfill \break
\noindent\textbf{Categories and Subject Descriptors:} H.3.4 [\textbf{Information Storage and Retrieval}]: Systems and Software.


\noindent\textbf{General Terms:} Experimentation, Human Factors.


\noindent\textbf{Keywords:} Question-answering, reputation, value prediction.

%\begin{IEEEkeywords}
%component, formatting, style, styling, insert
%\end{IEEEkeywords}

\input{tex/intro}

\input{tex/relatedwork}

\input{tex/dataset}

\input{tex/descripttasks}

\input{tex/communitydynamicsforQA}

\input{tex/predictiontasks}


\input{tex/conclusions}


\bibliographystyle{IEEEtran}
\bibliography{ref}


\vspace{12pt}

\end{document}
